### 2019-11-11 cvpr_submission/experiments.tex
Rewrote CLEVR subsection in the Experiments section.

\subsection{Generalization capabilities}

>>>>

\subsection{Multi-task learning}

\subsubsection{CLEVR tasks}
\vm{Will have to rephrase this in accordance with Jayram's definition.}

We have trained SAMNet using MI-Prometheus~\cite{kornuta2018accelerating}, a framework based on PyTorch~\cite{paszke2017automatic}, on the training set of the condition A of the CLEVR dataset (CLEVR-CoGenT)~\cite{johnson2017clevr}.
For all experiments, the training procedure is as follows: we train the model for 20 epochs on 90\% of the training set of CoGenT. We keep the remaining 10\% for validating the model at every epoch, and use the original validation sets (CoGenT-A  \& -B) as test sets. We used NVIDIA's GeForce GTX TITAN X GPUs.

We consider as task groups the question categories defined by the authors: \textit{Exist}, \textit{Count}, \textit{CompareInteger}, \textit{CompareAttribute}, \textit{QueryAttribute}. In order to investigate the potential benefits of multi-task learning, we conducted the following experiments:

\begin{itemize}
	\item We first trained SAMNet on a single task group, and tested on this same task group. These 5 experiments (one per task group) fit into the traditional Deep Learning procedure of training and testing on the same task, or on samples drawn from the same distribution over an input domain (single-task learning).
	\item Following, we trained SAMNet on all task groups jointly, and evaluated its performance on each group separately. The underlying hypothesis for this experiment is that learning jointly on all task groups would improve the performance on each task group.
	\item Finally, we finetuned a model, trained on all task groups jointly, on each of the task groups separately. We are interested in two observations here: how significant is the performance gain, if any, on the finetuned task? And complementary, how significant is the performance drop, if any, on the other tasks? 
\end{itemize}

The results of these experiments are available in \Tab{tab:CoGenT_results}. 
\begin{table}[htb]
	\centering
	\noindent
	\caption{CLEVR-CoGenT accuracies for all 5 tasks when training on solely one task, jointly training on all tasks and finetuning on each task. For all experiments, the validation and test sets are identical.}\label{tab:CoGenT_results}
	\begin{adjustbox}{width=0.5\textwidth}
	\begin{tabular}{c c c c c c c }\toprule
		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{\textbf{Test Accuracy (\%)}} \\  
		\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{on \texttt{valA} -- 150,000 samples} \\ 
		\cmidrule(lr){2-7}
		\multicolumn{1}{ c }{\textbf{Experiments}} & \textbf{Overall}& \textbf{Exist}  & \textbf{Count} & \textbf{CompareInteger} & \textbf{CompareAttribute} & \textbf{QueryAttribute}\\ 
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}
		\multicolumn{1}{ c }{Exist only} & 26.07 & 74.20	& 0.0	& 59.79	& 59.15 & 0.0 \\ 
		\multicolumn{1}{ c }{Count only} & 14.89  & 0.0	& 62.78	& 0.0 & 0.0 & 0.0 \\ 
		\multicolumn{1}{ c }{CompareInteger only} & 23.44 & 48.15	& 0.0	& 77.98	& 54.08 & 0.0 \\ 
		\multicolumn{1}{ c }{CompareAttribute only} & 23.50 & 51.93	& 0.0 & 59.06 & 61.73 & 0.0 \\ 
		\multicolumn{1}{ c }{QueryAttribute only} & 34.64 	& 0.0	& 0.0	& 0.0 & 0.0 & 97.08 \\ 		
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}

		\multicolumn{1}{ c }{All tasks} & 95.32 & 98.4 	& 86.75	& 96.0	& 98.65	& 98.02 \\ 
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-7}

		\multicolumn{1}{ c }{\textit{Trained on all tasks -- Finetune on $t$}} & &  & &  & &\\ 
		\multicolumn{1}{ c }{Exist} &  & & & & & \\ 
		\multicolumn{1}{ c }{Count} &  & & & & & \\
		\multicolumn{1}{ c }{CompareInteger} &  & & & & & \\
		\multicolumn{1}{ c }{CompareAttribute} &  & & & & & \\
		\multicolumn{1}{ c }{QueryAttribute} &  & & & & & \\

		\bottomrule
	\end{tabular}
    \end{adjustbox}
\end{table}

Looking at the first section of \tab{tab:CoGenT_results}, we observe, unsurprisingly, that a model trained on a single task will do better on this task than on the others when being tested. Nevertheless, we also note that a model, trained on \textit{Exist} only, obtains a score slightly better than random on \textit{CompareInteger} \& \textit{CompareAttribute}. This is due to the fact that these 3 task groups share the same labels space ('yes', 'no'). \textit{Count} and \textit{QueryAttribute} have isolated labels space (('0', '1', '2', '3', '4', '5', '6', '7', '8', '9', '10') and the set of object attributes values respectively) and we thus observe an accuracy of zero for these tasks, except when trained on these.

Training SAMNet on all tasks jointly, then testing it on each task, shows significant improvement on 4 out of 5 tasks, ranging from 18 points to 37 points. \textit{QueryAttribute} does not benefit from such an improvement, only seeing an increase of one point in terms of test accuracy. This suggests that \textit{QueryAttribute} is \textit{self-sufficient}, as the model is performing similarly between single-task learning and multi-task learning.

Finally, we finetuned the model trained on all tasks on each task separately, for up to one epoch. The interest here is to observe if finetuning on a specific task can further boost the accuracy on this particular, while preserving the performance on other tasks (and thus the overall performance as well) similar.

\begin{table}[htb]
	\centering
	\noindent
	\begin{adjustbox}{width=0.5\textwidth}
		\begin{tabular}{c c c c c c c }\toprule
			\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{\textbf{Test Accuracy (\%)}} \\  
			\multicolumn{1}{c }{\textbf{}} & \multicolumn{6}{c }{on \texttt{valA} -- 150,000 samples} \\ 
			\cmidrule(lr){2-7}
			\multicolumn{1}{ c }{\textbf{Experiments}} & \textbf{Overall}& \textbf{Exist}  & \textbf{Count} & \textbf{CompareInteger} & \textbf{CompareAttribute} & \textbf{QueryAttribute}\\ 
			\cmidrule(lr){1-1}
			\cmidrule(lr){2-7}
			\multicolumn{1}{ c }{All tasks but Exist} & 90.33 	& 60.42	& 86.12	& 96.18	& 98.52 & 98.60 \\ 
			\multicolumn{1}{ c }{All tasks but Count} & 74.59 	& 97.51	& 0.0	& 94.37	& 98.42 & 98.47 \\ 
			\multicolumn{1}{ c }{All tasks but CompareInteger} & 91.53 	& 98.22	& 86.09	& 56.35	& 98.78 & 98.40 \\ 
			\multicolumn{1}{ c }{All tasks but CompareAttribute} & 81.92 	& 98.32	& 86.36	& 95.86	& 23.18 & 98.44 \\ 
			\multicolumn{1}{ c }{All tasks but QueryAttribute} & 42.17 	& 76.79	& 54.64	& 79.87 & 64.13 & 0.0 \\

			\cmidrule(lr){1-1}
			\cmidrule(lr){2-7}
			\multicolumn{1}{ c }{\textbf{Trained on all tasks but $t$ -- Finetune on $t$ }} & &  & &  & &\\ 
			\multicolumn{1}{ c }{Exist} & 86.24 & 98.04 & 56.59 & 87.99 & 94.17 & 97.14 \\ 
			\multicolumn{1}{ c }{Count} & 46.97 & 2.80 & 78.73 & 15.60 & 35.06 & 56.60 \\
			\multicolumn{1}{ c }{CompareInteger} & 73.46 & 72.89 & 42.42 & 92.07 & 68.32 & 91.90 \\
			\multicolumn{1}{ c }{CompareAttribute} & 48.16 & 85.77 & 30.84 & 77.20 & 97.72 & 13.21 \\
			\multicolumn{1}{ c }{QueryAttribute} & 35.26 & 38.65 & 4.22 & 31.56 & 5.08 & 70.67 \\
		\bottomrule
	\end{tabular}
\end{adjustbox}
\caption{CoGenT accuracies with finetuning.}\label{tab:CoGenT_finetuning_results}
\end{table}

End of section
